%-------------------------
% Resume in Latex
% Author : Cuixiaochen
% Website: https://cuixiaochen.com/
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} - #2 \\
    \end{tabular*}
    \jobTitle
        {#3} {#4}
}

\newcommand{\jobTitle}[2]{
    \textit{\small#1} \textit{\small(#2)} \\
}

\newcommand{\resumeSubheadingLong}[8]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} - #2 \\
    \end{tabular*}
    \jobTitle
        {#3} {#4}\vspace{-2pt}
    \jobTitle
        {#5} {#6}\vspace{-2pt}
    \jobTitle
        {#7} {#8}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Xiaochen Cui}\\
  \href{https://cuixiaochen.com}{blog: \underline{XiaochenCui's Blog}} & email: \href{mailto:jcnlcxc.new@gmail.com}{\underline{jcnlcxc.new@gmail.com}}\\
  \href{https://github.com/XiaochenCui}{github: \underline{XiaochenCui}} & mobile: (+86) 188-0224-3655
\end{tabular*}



%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Shanghai Magus Technology Co., Ltd.}{Chongqing, China}
      {Senior Software Engineer}{Apr 2021 - Present}
      \resumeItemListStart
        \resumeItem{Vectorized Query Engine}
          {Designed and developed the vectorized query engine for LightningDB, which makes almost all kinds of queries become 20-100 times faster. (LightningDB is a column-oriented DBMS for online analytical processing.)}
        \resumeItem{Designed the Structure of Underlying Storage Files}
          {Designed the structure of data files and index files for underlying storage, resulted in a 70\% reduction in disk footprint and a nearly 4x increase in system IO speed.}
        \resumeItem{Continuous Integration System}
          {Built a CI system that reduced the number of bugs in the system by half and increased the speed of bug resolution by two.}
      \resumeItemListEnd

    \resumeSubheadingLong
      {Burnish Technology}{Chongqing, China}
      {Senior Software Engineer}{2020}
      {Software Engineer}{2019}
      {Junior Software Engineer}{2018}
      \resumeItemListStart
        \resumeItem{High Performance Gateway}
          {A high performance TCP Gateway used for receive ioT packages, with built-in features such as connection management and instructions sending.}
        \resumeItem{Command Management Component}
          {Manage the complete life cycle of downstream instructions, including instructions sending, retry, status recording, result reporting, etc.}
        \resumeItem{Package Forwarder}
          {Forward ioT packages to other components (or other platforms), with real-time filtering feature.}
        \resumeItem{Cloud Native}
          {Bringing in the cloud native ecology to the company, including kubernetes, prometheus, grafana, consul, k8s operator, opentracing, etc.}
        \resumeItem{System Tuning}
          {The design and optimization of the cache layer. Program profiling for golang/python components.}
        \resumeItem{Alluxio}
          {The technical research, setup and maintenance of Alluxio.}
      \resumeItemListEnd

    \resumeSubheading
      {Zhicheng Technology}{Chengdu, China}
      {Senior Software Engineer}{Aug 2017 - Jan 2018}
      \resumeItemListStart
        \resumeItem{Backend Development}
          {Write back-end logic using python (Django, Twisted, etc).}
        \resumeItem{Operation}
          {The deployment, operation and maintenance of various services.}
        \resumeItem{Recruitment}
          {Recruitment of backend developers.}
        \resumeItem{Management}
          {Formulate development specifications for the development team such as the git work flow, format for requests and response, coding style, etc.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{simple-db-java}
      {A simple relational database written based on mit6.830, which implemented buffer pool, write ahead log, transaction, roll-back, etc. Support underlying storage with heap format and b+ tree format. \href{https://github.com/XiaochenCui/simple-db-hw}{https://github.com/XiaochenCui/simple-db-hw}}
    \resumeSubItem{simple-db-rust}
      {A simple relational database written in rust, still under development.
      \href{https://github.com/XiaochenCui/simple-db-rust/}{https://github.com/XiaochenCui/simple-db-rust/}}
    \resumeSubItem{distributed key-value storage}
      {A fault-tolerance key-value storage based on raft consensus algorithm. 
      \href{https://github.com/XiaochenCui/mit6.824}{https://github.com/XiaochenCui/mit6.824}}
  \resumeSubHeadingListEnd
  
%-----------Courses-----------------
\section{Courses and Papers studied}
  \resumeSubHeadingListStart
    \resumeSubItem{MIT6.828: Operation Systems}
      {\href{https://pdos.csail.mit.edu/6.828/2018/}{https://pdos.csail.mit.edu/6.828/2018/}}
    \resumeSubItem{MIT6.830: Database Systems}
      {\href{http://dsg.csail.mit.edu/6.830/}{http://dsg.csail.mit.edu/6.830/}}
    \resumeSubItem{MIT6.824: Distributed Systems}
      {\href{https://pdos.csail.mit.edu/6.824/}{https://pdos.csail.mit.edu/6.824/}}
    \resumeSubItem{Cryptography I}
      {\href{https://www.coursera.org/learn/crypto}{https://www.coursera.org/learn/crypto}}
    \resumeSubItem{UICD CS 241: System Programming}
      {\href{http://cs241.cs.illinois.edu/}{http://cs241.cs.illinois.edu/}}
    \resumeSubItem{And Some Papers}
      {\href{https://cuixiaochen.com/posts/system-research-syllabus/}{https://cuixiaochen.com/posts/system-research-syllabus/}}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Python, Go, Rust, C++, Java}
   }
   \item{
     \textbf{Technologies}{: Cloud Native Operation, Linux Operation, Database Development }
   }
 \resumeSubHeadingListEnd
 

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tiangong University}{Tianjin, China}
      {Bachelor of Software Engineering}{Sep. 2013 -- Jun. 2017}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
